---
title: "Mitchelle's EDA"
output: pdf_document
date: "2023-11-01"
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r libraries}
library(readr)
library(dplyr)
library(ggplot2)
library(tidyverse)
library(invgamma)
library(knitr)
library(stringr)
library(fitdistrplus)
library(kableExtra)
library(cowplot)
```


#Data
```{r data}
data_2017_2021 <- read_csv("Cleaned Data/data_2017_2021.csv")
data_2022_2023 <- read_csv("Cleaned Data/data_2022_2023.csv") %>% 
  drop_na(Score, E_Score, D_Score, Apparatus, Round, Location, Competition, Country, Gender)

```

```{r}
#remove gymnasts that did not have Scores??
data_2017_2021 %>% 
  filter(is.na(Score)) %>% 
  dplyr::summarise(ct = n())

data_2022_2023 %>% 
  filter(is.na(Score)) %>% 
  dplyr::summarise(ct = n())
```

```{r}
#Competitions types
data_2017_2021 %>% 
  group_by(Competition) %>% 
  dplyr::summarise(ct = n())

data_2022_2023 %>% 
  group_by(Competition) %>% 
  dplyr::summarise(ct = n())
```

```{r}
data_2017_2021 %>% 
  group_by(Round) %>% 
  dplyr::summarise(ct = n())

data_2022_2023 %>% 
  group_by(Round) %>% 
  dplyr::summarise(ct = n())
```
#HERE
```{r}
data_2022_2023 %>% 
  group_by(Competition,Round,Apparatus, Rank) %>% 
  dplyr::summarise(ct = n())
```


```{r}
data_2017_2021 %>% 
  group_by(Apparatus) %>% 
  dplyr::summarise(ct = n())

data_2022_2023 %>% 
  group_by(Apparatus) %>% 
  dplyr::summarise(ct = n())
```


```{r}
# fix first name issue (some have middle names)
```


```{r}
#women 2017-2021 data 
women2017_2021 <- data_2017_2021[data_2017_2021$Gender == "w", ]
#there is no men data in 2017-2021 data table

#women 2022-2023 data
women2022_2023 <- data_2022_2023[data_2022_2023$Gender == "w", ]
#men 2022-2023 data
men2022_2023 <- data_2022_2023[data_2022_2023$Gender == "m", ]

#women USA data 2017-2021
womenUSA2017_2021 <- data_2017_2021[data_2017_2021$Gender == "w"& data_2017_2021$Country == "USA",]


#USA men 2022-2023 data
menUSA2022_2023 <- data_2022_2023[data_2022_2023$Gender == "m"& data_2022_2023$Country == "USA",]
#USA women 2022-2023 data
womenUSA2022_2023 <- data_2022_2023[data_2022_2023$Gender == "w"& data_2022_2023$Country == "USA",]

```

```{r}
 ggplot(data = womenUSA2017_2021, aes(x = Apparatus, y = Score)) +
  geom_boxplot() +
  labs(title = "USA Scores by Apparatus", x = "Appartus", y = "Total Score") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) + facet_wrap(~Round)

 ggplot(data = menUSA2022_2023, aes(x = Apparatus, y = Score)) +
  geom_boxplot() +
  labs(title = "USA Scores by Apparatus", x = "Appartus", y = "Total Score") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) + facet_wrap(~Round)

 ggplot(data = womenUSA2022_2023, aes(x = Apparatus, y = Score)) +
  geom_boxplot() +
  labs(title = "USA Scores by Apparatus", x = "Appartus", y = "Total Score") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) + facet_wrap(~Round)
```

```{r}
 ggplot(data = women2017_2021, aes(x = Apparatus, y = Score)) +
  geom_point() +
  labs(title = "Scores by Apparatus for Women (2017-2021)", x = "Appartus", y = "Total Score") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

 ggplot(data = women2022_2023, aes(x = Apparatus, y = Score)) +
  geom_point() +
  labs(title = "Scores by Apparatus for Women(2022-2023)", x = "Appartus", y = "Total Score") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
 
  ggplot(data = men2022_2023, aes(x = Apparatus, y = Score)) +
  geom_point() +
  labs(title = "Scores by Apparatus for Men (2022-2023)", x = "Appartus", y = "Total Score") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
 
```
```{r}
data_2022_2023 %>% 
  group_by(Competition, Round, Rank) %>% 
  dplyr::summarise(ct = n())
```

So far we subsetted the top 20% percentile by Gender and Apparatus
```{r}
#take out middle names because some names have first name and some have middle (Frederick (Nathaniel) Richard)
data_2022_2023$FirstNameOnly <- sub("^(\\w+)\\s+\\w+$", "\\1", data_2022_2023$FirstName)
```


```{r}
#subsetting 2nd data set by individual athlete
data_2022_2023 %>% 
  group_by(Gender,Competition,Round,Apparatus, Rank) %>% 
  dplyr::summarise(ct = n())

data_2022_2023 %>% 
  group_by(Gender, Apparatus) %>% 
  mutate(meanScore = mean(Score))
```
```{r}
data_2022_2023 %>% 
  group_by(Gender,Apparatus) %>% 
  mutate()
  summarise(meanScore =  mean(Score))
```


```{r}
data_2022_2023 %>% 
  filter(Country == 'USA') %>% 
  group_by(LastName,FirstName) %>% 
  dplyr::summarise(sum = n())
```
# Final Submission Work

```{r}
laterdata <- read_csv("Cleaned Data/data_2022_2023.csv")
later <- laterdata |>
  drop_na(Score, E_Score, D_Score, Apparatus, Round, Location, Competition, Country, Gender)
```

```{r}
#indonesian gymnast's name is Abiyu RAFI not ABIYURAFI
laterdata <- laterdata |>
  mutate(FirstName = ifelse(LastName == "ABIYURAFI" & FirstName == ".", "Abiyu", FirstName),
    LastName = ifelse(LastName == "ABIYURAFI", "RAFI", LastName))


laterdata <- laterdata |>
  mutate(firstname_check = ifelse(str_length(FirstName) >= 3, 1, 0),
         lastname_check = ifelse(str_length(LastName) >= 3, 1, 0))

laterdata <- laterdata |>
  mutate(FirstName = ifelse(firstname_check == 0, paste0(FirstName, "_"), FirstName),
         LastName = ifelse(lastname_check == 0, paste0(LastName, "_"), LastName))

#based on string methods -- creating unique athlete IDs
laterdata <- laterdata |>
  mutate(unique_id = paste0(str_sub(FirstName, 1, 3), str_sub(LastName, 1, 3), "_", Country))

#create a vector for AA or team
AA_team <- c("AAfinal", "TeamFinal", "TeamQual", "AAqual")
'%notin%' <- function(x,y)!('%in%'(x,y))

finals_vector <- c("AAfinal", "TeamFinal", "final")

#these quantiles are already grouped by gender and competition, round, apapratus, etc. so no bleeding
quantiled_data <- laterdata |>
  group_by(Gender, Competition, Round, Apparatus) |>
  mutate(quantile_20s = ntile(-Score, 5),
         quantile_10s = ntile(-Score, 10))

#filter out the athletes who have NEVER made it to a final, ever
filtered_data <- quantiled_data |>
  group_by(unique_id) |>
  filter(any(Round == "final" | Round == "TeamFinal" | Round == "AAfinal")) |>
  ungroup()

#summary of number of athletes competed in each competition in each round
number_athletes <- filtered_data |>
  group_by(Competition, Round) |>
  summarise(athletes_participated = n_distinct(unique_id))


# at the oceania continental championships, only 10 unique athletes competed
# every other competition at each round has at minimum 36 athletes competing
#at these final rounds, there are at least 40 athletes in each final, so it's fine
#going to left join to show the number of athletes that participated per round

joined_data <- filtered_data |>
  left_join(number_athletes, by = c("Competition", "Round"))

#now the athletes_participated column = how many athletes competed in it


#this filters out the individual records for ppl who were not in top quantiles at a competition
final_data <- joined_data |>
  filter((athletes_participated <= 100 & quantile_20s == 1) | (athletes_participated > 100 & quantile_10s == 1) | (Competition == "Oceania Continental Championships 2023" & quantile_20s %in% c(1, 2)))

#now let's check the number of unique athletes left
# final_data |>
#   group_by(Country) |>
#   summarise(athletes_left = n_distinct(unique_id))

#there are 679 athletes left in total once we have filtered, USA still has 91 left
```

```{r}
menOG <- data_2022_2023 %>% 
  filter(Gender == 'm') %>% 
  mutate(USA = ifelse(Country == 'USA', TRUE, FALSE))
  
womenOG <- data_2022_2023 %>% 
  filter(Gender == 'w') %>% 
  mutate(USA = ifelse(Country == 'USA', TRUE, FALSE))
```

```{r}
ggplot(data = menOG, aes(x = Score, group = USA, fill = USA)) + geom_density(adjust = 1.5) + facet_wrap(~Round) + labs(title = "Men's Score Density by Event Type", subtitle = "USA vs Non-USA")

ggplot(data = womenOG, aes(x = Score, group = USA, fill = USA)) + geom_density(adjust = 1.5) + facet_wrap(~Round) + labs(title = "Women's Score Density by Event Type", subtitle = "USA vs Non-USA")
```
## Original Data
The USA men's teams tend to have a greater concentration in higher scores than
non USA competitors in individual qualifiers as well team qualifiers and finals.
This shows that for the men's team our model should prioritize the team all 
around events.

The USA women's teams tend to have a greater concentration in higher scores than
non USA competitors in all rounds, but especially more so in team all around.
Individual apparatuses are also a great focus since that would maximize the actual
medal count and team USA tends to have higher scores than non USA competitors.


## Finalized Data
```{r}
menFinal <- final_data %>% 
  filter(Gender == 'm')

womenFinal <- final_data %>% 
  filter(Gender == 'w')
```

```{r}
#make a USA and nonUSA factored column
menFinal <- menFinal %>% 
  mutate(USA = ifelse(Country == 'USA', TRUE, FALSE))
womenFinal <- womenFinal %>% 
  mutate(USA = ifelse(Country == 'USA', TRUE, FALSE))
```

```{r}
ggplot(data = menFinal, aes(x = Score, group = USA, fill = USA)) + geom_density(adjust = 1.5) + facet_wrap(~Round) + labs(title = "Men's Score Density by Event Type (Finalized Data)", subtitle = "USA vs Non-USA")

ggplot(data = womenFinal, aes(x = Score, group = USA, fill = USA)) + geom_density(adjust = 1.5) + facet_wrap(~Round) + labs(title = "Women's Score Density by Event Type (Finalized Data)", subtitle = "USA vs Non-USA")
```
For the men's densities we can see that the USA athletes have more concentration on
higher scores than non USA teams for the individual qualifying and team qualifying round.

For the women's denities there is more concentration on higher scores for the USA
team for both individual apparatus rounds (final and qualifying) as well as
the team qualifiers. Which futher proves our model should focus on a mixture of both
but heavily prioritize the individual appartuses.

# NEW RANKING
## Men
```{r}
#rank actually shown to be correct here for the early observations
orderMenFinal <- menFinal %>% 
  arrange(Competition, Round, Apparatus, desc(Score)) %>% 
  dplyr::select(unique_id, Country,Competition, Round,Apparatus, Rank, Score)
orderMenFinal
```
### Men's Ranking System
```{r}
#this ranking works works to individually rank the observations rather than taking into account team/all around sum score rankings since we are aiming to choose best individual atheletes
#also important to note that rankers did not give same scores the same rank, but this will be done in new rank
orderMenFinal <- orderMenFinal %>%
  mutate(newRank = NA)
orderMenFinal$newRank[1] <- 1

for (i in 2:nrow(orderMenFinal)){
  if ((orderMenFinal$Competition[i] == orderMenFinal$Competition[i-1]) & (orderMenFinal$Round[i] == orderMenFinal$Round[i-1]) & (orderMenFinal$Apparatus[i] == orderMenFinal$Apparatus[i-1]) & (orderMenFinal$Score[i] == orderMenFinal$Score[i-1])) {
    orderMenFinal$newRank[i] <- orderMenFinal$newRank[i-1]
  } 
  else if ((orderMenFinal$Competition[i] == orderMenFinal$Competition[i-1]) & (orderMenFinal$Round[i] == orderMenFinal$Round[i-1]) & (orderMenFinal$Apparatus[i] == orderMenFinal$Apparatus[i-1])) {
    orderMenFinal$newRank[i] <- orderMenFinal$newRank[i-1]+1
  }
  else {
    orderMenFinal$newRank[i] <- 1
  }
}
orderMenFinal
```


#Women
```{r}
orderWomenFinal <- womenFinal %>% 
  arrange(Competition, Round, Apparatus, desc(Score)) %>% 
  dplyr::select(unique_id, Country,Competition, Round,Apparatus, Rank, Score)
orderWomenFinal
```
### Women's Ranking System
```{r}
#this ranking works works to individually rank the observations rather than taking into account team/all around sum score rankings since we are aiming to choose best individual atheletes
#also important to note that rankers did not give same scores the same rank, but this will be done in new rank
orderWomenFinal <- orderWomenFinal %>%
  mutate(newRank = NA)
orderWomenFinal$newRank[1] <- 1

for (i in 2:nrow(orderWomenFinal)){
  if ((orderWomenFinal$Competition[i] == orderWomenFinal$Competition[i-1]) & (orderWomenFinal$Round[i] == orderWomenFinal$Round[i-1]) & (orderWomenFinal$Apparatus[i] == orderWomenFinal$Apparatus[i-1]) & (orderWomenFinal$Score[i] == orderWomenFinal$Score[i-1])) {
    orderWomenFinal$newRank[i] <- orderWomenFinal$newRank[i-1]
  } 
  else if ((orderWomenFinal$Competition[i] == orderWomenFinal$Competition[i-1]) & (orderWomenFinal$Round[i] == orderWomenFinal$Round[i-1]) & (orderWomenFinal$Apparatus[i] == orderWomenFinal$Apparatus[i-1])) {
    orderWomenFinal$newRank[i] <- orderWomenFinal$newRank[i-1]+1
  }
  else {
    orderWomenFinal$newRank[i] <- 1
  }
}
orderWomenFinal
```
## Simulations

```{r removing-obs, message = FALSE}
#summary stats for each athlete for each apparatus
combined_apparatus <- combined_final |>
  group_by(Apparatus, unique_id, Country, Gender) |>
  summarise(mean_score = mean(Score),
            var_score = var(Score),
            number_obs = n(),
            mean_D = mean(D_Score),
            var_D = var(D_Score),
            mean_E = mean(E_Score),
            var_E = var(E_Score)) |>
  filter(number_obs >= 3)

combined <- combined_final |>
  left_join(combined_apparatus, by = c("Apparatus", "unique_id", "Country", "Gender"))

# USE THIS DF FOR RUNNING SIMS
combined <- combined |>
  filter(!is.na(number_obs))

#combined now has 2689 obs instead of 4040 obs -- using this to run sims
```

```{r fitting-priors}
fit_normal_priors <- function(data, apparatus, gender) {
  #fitting normal prior for mean scores
  normal_mu_fit <- fitdist(data$mean_score, "norm")
  #fitting inv gamma prior for variance of scores
  invgamma_var_fit <- fitdist(data$var_score, "invgamma")
  
  m_0 <-  normal_mu_fit$estimate[[1]]
  sig_0 <- normal_mu_fit$estimate[[2]]
  k_0 <- invgamma_var_fit$estimate[[1]] 
  v_0 <- invgamma_var_fit$estimate[[2]]

  return(c(m_0 = m_0, sig_0 = sig_0, k_0 = k_0, v_0 = v_0))
}
```

```{r simulation-function}
#code for simulations, inspired by STA360/peter hoff textbook

analyze_athlete <- function(athlete_results, m_0, sig_0, k_0, v_0, smc = 1000) {
  n <- length(athlete_results)
  ybar <- mean(athlete_results)
  var <- var(athlete_results)
  
  #NEED TO CHECK THIS BAYESIAN
  k_n <- k_0 + n
  v_n <- v_0 + n
  m_n <- (k_0*m_0 + n*ybar)/k_n
  sig_n <- (v_0*sig_0 + (n-1)*var + k_0*n*(ybar - m_0)**2/k_n)/v_n
  sig_sample <- mean(rinvgamma(smc, v_n/2, sig_n*v_n/2))
  theta_sample <- mean(rnorm(smc, m_n, sqrt(sig_sample/k_n)))
  
  return(c(theta_sample, sig_sample))
}
```

```{r creating-medals}
# So this represents one simulation, we could probably run this like 1000 times and average out the medal counts
simulate_results <- function(data, apparatus, gender, m_0, sig_0, k_0, v_0, medals = TRUE) {
  simul_data <- data %>%
    filter(Apparatus == apparatus
           , Gender == gender) %>%
    group_by(unique_id) %>%
    summarise(mean_estimate = analyze_athlete(Score, m_0 = m_0, sig_0 = sig_0, k_0 = k_0, v_0 = v_0)[1],
              var_estimate = analyze_athlete(Score, m_0 = m_0, sig_0 = sig_0, k_0 = k_0, v_0 = v_0)[2],
              observations = n(), .groups = "keep") %>%
    rowwise() %>%
    mutate(simulated_Score = rnorm(1, mean_estimate, var_estimate)) %>% # Truncate scores > 10
    mutate(simulated_Score = ifelse(simulated_Score > 20, 10, simulated_Score)) %>% # Truncate scores < 0
    mutate(simulated_Score = ifelse(simulated_Score < 0, 0, simulated_Score)) 
  
  if (medals == TRUE) {
    # order by top 3 results and assign gold, silver, bronze
    simul_data <- simul_data %>%
      ungroup() %>%
      arrange(desc(simulated_Score)) %>%
      mutate(medal = case_when(row_number() == 1 ~ "Gold",
                               row_number() == 2 ~ "Silver",
                               row_number() == 3 ~ "Bronze",
                               TRUE ~ "NA"))
    
  }
  return(simul_data)
}
```

```{r competition-simulation }
# full competition simulation, gets pretty slow with 1000 simulations
simulate_full_competition <- function(data, apparatus, gender, mu_0, sig_0, k_0, v_0, smc) {
  athletes_medals <- data %>%
    dplyr::select(unique_id) %>%
    distinct() %>%
    mutate(Golds = 0, Silvers = 0, Bronzes = 0, Total_Medals = 0)
  
  for (i in 1:smc) {    
    big_simul <- simulate_results(data, apparatus, gender, mu_0, sig_0, k_0, v_0, TRUE) %>%
      filter(medal != "NA")
    
    big_simul <- big_simul %>%
      group_by(unique_id) %>%
      summarise(Golds = sum(medal == "Gold"),
                Silvers = sum(medal == "Silver"),
                Bronzes = sum(medal == "Bronze"),
                Total_Medals = sum(medal != "NA"),
                .groups = "keep") %>%
      ungroup()
    
    athletes_medals <- athletes_medals %>%
      left_join(big_simul, by = c("unique_id")) %>%
      mutate(Golds = ifelse(is.na(Golds.y), Golds.x, Golds.y + Golds.x),
             Silvers = ifelse(is.na(Silvers.y), Silvers.x, Silvers.y + Silvers.x),
             Bronzes = ifelse(is.na(Bronzes.y), Bronzes.x, Bronzes.y + Bronzes.x),
             Total_Medals = ifelse(is.na(Total_Medals.y), Total_Medals.x, Total_Medals.y + Total_Medals.x)) %>%
      dplyr::select(unique_id, Golds, Silvers, Bronzes, Total_Medals) %>%
      arrange(desc(Total_Medals))
  } 
  return(athletes_medals)
}
```

## Female Athletes' Results

### Women's Apparatuses:
- FX: floor exercise
- PH: pommel hours
- SR: still rings
- VT: vault
- PB: parallel bars
- HB: high bar

```{r FX-womens-sims}
set.seed(123)

prior_parameters <- suppressWarnings(fit_normal_priors(combined_apparatus, "FX", "w"))
print(prior_parameters)

mu_0 <- prior_parameters[1]
sig_0 <- prior_parameters[2]
k_0 <- prior_parameters[3]
v_0 <- prior_parameters[4]

FX_w_simul <- simulate_full_competition(combined, "FX", "w", mu_0, sig_0, k_0, v_0, 500)

FX_w_simul |>
  head(10) |>
  kable(caption = "Women's Floor Exercise Simulation Results ", col.names = c("Athlete", "Golds", "Silvers", "Bronzes", "Total Medals")) |>
  kable_styling(font_size = 9, latex_options = "HOLD_position")
```

```{r}
#Creates country variable
FX_w_simul$Country <- factor(sub(".+_([A-Z]+)", "\\1", FX_w_simul$unique_id))
#adds medal weight variable
FX_w_simul$Medal_Weight <- (FX_w_simul$Golds*3) + (FX_w_simul$Silvers*2) + (FX_w_simul$Bronzes*1)
#adds apparatus to facet by later on in visuals
FX_w_simul$Apparatus <- "FX"
FX_w_simul
```

```{r BB-womens-sims}
set.seed(123)

prior_parameters <- suppressWarnings(fit_normal_priors(combined_apparatus, "BB", "w"))
print(prior_parameters)

mu_0 <- prior_parameters[1]
sig_0 <- prior_parameters[2]
k_0 <- prior_parameters[3]
v_0 <- prior_parameters[4]

BB_w_simul <- simulate_full_competition(combined, "BB", "w", mu_0, sig_0, k_0, v_0, 100)
BB_w_simul |>
  head(10) |>
  kable(caption = "Women's Balance Beam Simulation Results ", col.names = c("Athlete", "Golds", "Silvers", "Bronzes", "Total Medals")) |>
  kable_styling(font_size = 9, latex_options = "HOLD_position")
```

```{r}
#Creates country variable
BB_w_simul$Country <- factor(sub(".+_([A-Z]+)", "\\1", BB_w_simul$unique_id))
#adds medal weight variable
BB_w_simul$Medal_Weight <- (BB_w_simul$Golds*3) + (BB_w_simul$Silvers*2) + (BB_w_simul$Bronzes*1)
#adds apparatus to facet by later on in visuals
BB_w_simul$Apparatus <- "BB"
BB_w_simul
```


```{r VT-womens-sims}
set.seed(123)

prior_parameters <- suppressWarnings(fit_normal_priors(combined_apparatus, "VT", "w"))
print(prior_parameters)

mu_0 <- prior_parameters[1]
sig_0 <- prior_parameters[2]
k_0 <- prior_parameters[3]
v_0 <- prior_parameters[4]

VT_w_simul <- simulate_full_competition(combined, "VT", "w", mu_0, sig_0, k_0, v_0, 100)
VT_w_simul |>
  head(10) |>
  kable(caption = "Women's Vault Simulation Results ", col.names = c("Athlete", "Golds", "Silvers", "Bronzes", "Total Medals")) |>
  kable_styling(font_size = 9, latex_options = "HOLD_position")
```

```{r}
#Creates country variable
VT_w_simul$Country <- factor(sub(".+_([A-Z]+)", "\\1", VT_w_simul$unique_id))
#adds medal weight variable
VT_w_simul$Medal_Weight <- (VT_w_simul$Golds*3) + (VT_w_simul$Silvers*2) + (VT_w_simul$Bronzes*1)
#adds apparatus to facet by later on in visuals
VT_w_simul$Apparatus <- "VT"
VT_w_simul
```

```{r UB-women-sims}
set.seed(123)

prior_parameters <- suppressWarnings(fit_normal_priors(combined_apparatus, "UB", "w"))
print(prior_parameters)

mu_0 <- prior_parameters[1]
sig_0 <- prior_parameters[2]
k_0 <- prior_parameters[3]
v_0 <- prior_parameters[4]

UB_w_simul <- simulate_full_competition(combined, "UB", "w", mu_0, sig_0, k_0, v_0, 100)
UB_w_simul |>
  head(10) |>
  kable(caption = "Women's Uneven Bars Simulation Results ", col.names = c("Athlete", "Golds", "Silvers", "Bronzes", "Total Medals")) |>
  kable_styling(font_size = 9, latex_options = "HOLD_position")
```

```{r}
#Creates country variable
UB_w_simul$Country <- factor(sub(".+_([A-Z]+)", "\\1", UB_w_simul$unique_id))
#adds medal weight variable
UB_w_simul$Medal_Weight <- (UB_w_simul$Golds*3) + (UB_w_simul$Silvers*2) + (UB_w_simul$Bronzes*1)
#adds apparatus to facet by later on in visuals
UB_w_simul$Apparatus <- "UB"
UB_w_simul
```

```{r}
#Joins all women's medal results table for facet wrapping

#HAVE TO EVENTUALLY ADD VT1 and VT2!!
tot_w_simul <- bind_rows(FX_w_simul,BB_w_simul, VT_w_simul, UB_w_simul)
tot_w_simul <- tot_w_simul %>% 
  mutate(USA = as.factor(ifelse(Country == "USA", TRUE, FALSE)))
tot_w_simul
```



## Male Athletes' Results

### Men's Apparatuses:
- VT: vault
- UB: uneven bars
- BB: balance beam
- FX: floor exercise

```{r FX-men-sims}
set.seed(123)

prior_parameters <- suppressWarnings(fit_normal_priors(combined_apparatus, "FX", "m"))
print(prior_parameters)

mu_0 <- prior_parameters[1]
sig_0 <- prior_parameters[2]
k_0 <- prior_parameters[3]
v_0 <- prior_parameters[4]

FX_m_simul <- simulate_full_competition(combined, "FX", "m", mu_0, sig_0, k_0, v_0, 100)
FX_m_simul |>
  head(10) |>
  kable(caption = "Men's Floor Exercise Simulation Results ", col.names = c("Athlete", "Golds", "Silvers", "Bronzes", "Total Medals")) |>
  kable_styling(font_size = 9, latex_options = "HOLD_position")
```

```{r}
#Creates country variable
FX_m_simul$Country <- factor(sub(".+_([A-Z]+)", "\\1", FX_m_simul$unique_id))
#adds medal weight variable
FX_m_simul$Medal_Weight <- (FX_m_simul$Golds*3) + (FX_m_simul$Silvers*2) + (FX_m_simul$Bronzes*1)
#adds apparatus to facet by later on in visuals
FX_m_simul$Apparatus <- "FX"
FX_m_simul
```

```{r VT-men-sims}
set.seed(123)

prior_parameters <- suppressWarnings(fit_normal_priors(combined_apparatus, "VT", "m"))
print(prior_parameters)

mu_0 <- prior_parameters[1]
sig_0 <- prior_parameters[2]
k_0 <- prior_parameters[3]
v_0 <- prior_parameters[4]

VT_m_simul <- simulate_full_competition(combined, "VT", "m", mu_0, sig_0, k_0, v_0, 100)
VT_m_simul |>
  head(10) |>
  kable(caption = "Men's Vault Simulation Results ", col.names = c("Athlete", "Golds", "Silvers", "Bronzes", "Total Medals")) |>
  kable_styling(font_size = 9, latex_options = "HOLD_position")
```

```{r}
#Creates country variable
VT_m_simul$Country <- factor(sub(".+_([A-Z]+)", "\\1", VT_m_simul$unique_id))
#adds medal weight variable
VT_m_simul$Medal_Weight <- (VT_m_simul$Golds*3) + (VT_m_simul$Silvers*2) + (VT_m_simul$Bronzes*1)
#adds apparatus to facet by later on in visuals
VT_m_simul$Apparatus <- "VT"
VT_m_simul
```

```{r PH-men-sims}
set.seed(123)

prior_parameters <- suppressWarnings(fit_normal_priors(combined_apparatus, "PH", "m"))
print(prior_parameters)

mu_0 <- prior_parameters[1]
sig_0 <- prior_parameters[2]
k_0 <- prior_parameters[3]
v_0 <- prior_parameters[4]

PH_m_simul <- simulate_full_competition(combined, "PH", "m", mu_0, sig_0, k_0, v_0, 100)
PH_m_simul |>
  head(10) |>
  kable(caption = "Men's Pommel Horse Simulation Results ", col.names = c("Athlete", "Golds", "Silvers", "Bronzes", "Total Medals")) |>
  kable_styling(font_size = 9, latex_options = "HOLD_position")
```

```{r}
#Creates country variable
PH_m_simul$Country <- factor(sub(".+_([A-Z]+)", "\\1", PH_m_simul$unique_id))
#adds medal weight variable
PH_m_simul$Medal_Weight <- (PH_m_simul$Golds*3) + (PH_m_simul$Silvers*2) + (PH_m_simul$Bronzes*1)
#adds apparatus to facet by later on in visuals
PH_m_simul$Apparatus <- "PH"
PH_m_simul
```

```{r HB-men-sims}
set.seed(123)

prior_parameters <- suppressWarnings(fit_normal_priors(combined_apparatus, "HB", "m"))
print(prior_parameters)

mu_0 <- prior_parameters[1]
sig_0 <- prior_parameters[2]
k_0 <- prior_parameters[3]
v_0 <- prior_parameters[4]

HB_m_simul <- simulate_full_competition(combined, "HB", "m", mu_0, sig_0, k_0, v_0, 100)
HB_m_simul |>
  head(10) |>
  kable(caption = "Men's High Bar Simulation Results ", col.names = c("Athlete", "Golds", "Silvers", "Bronzes", "Total Medals")) |>
  kable_styling(font_size = 9, latex_options = "HOLD_position")
```

```{r}
#Creates country variable
HB_m_simul$Country <- factor(sub(".+_([A-Z]+)", "\\1", HB_m_simul$unique_id))
#adds medal weight variable
HB_m_simul$Medal_Weight <- (HB_m_simul$Golds*3) + (HB_m_simul$Silvers*2) + (HB_m_simul$Bronzes*1)
#adds apparatus to facet by later on in visuals
HB_m_simul$Apparatus <- "HB"
HB_m_simul
```

```{r SR-men-sims}
set.seed(123)

prior_parameters <- suppressWarnings(fit_normal_priors(combined_apparatus, "SR", "m"))
print(prior_parameters)

mu_0 <- prior_parameters[1]
sig_0 <- prior_parameters[2]
k_0 <- prior_parameters[3]
v_0 <- prior_parameters[4]

SR_m_simul <- simulate_full_competition(combined, "SR", "m", mu_0, sig_0, k_0, v_0, 100)
SR_m_simul |>
  head(10) |>
  kable(caption = "Men's Still Rings Simulation Results ", col.names = c("Athlete", "Golds", "Silvers", "Bronzes", "Total Medals")) |>
  kable_styling(font_size = 9, latex_options = "HOLD_position")
```

```{r}
#Creates country variable
SR_m_simul$Country <- factor(sub(".+_([A-Z]+)", "\\1", SR_m_simul$unique_id))
#adds medal weight variable
SR_m_simul$Medal_Weight <- (SR_m_simul$Golds*3) + (SR_m_simul$Silvers*2) + (SR_m_simul$Bronzes*1)
#adds apparatus to facet by later on in visuals
SR_m_simul$Apparatus <- "SR"
SR_m_simul
```

```{r PB-men-sims}
set.seed(123)

prior_parameters <- suppressWarnings(fit_normal_priors(combined_apparatus, "PB", "m"))
print(prior_parameters)

mu_0 <- prior_parameters[1]
sig_0 <- prior_parameters[2]
k_0 <- prior_parameters[3]
v_0 <- prior_parameters[4]

PB_m_simul <- simulate_full_competition(combined, "PB", "m", mu_0, sig_0, k_0, v_0, 100)
PB_m_simul |>
  head(10) |>
  kable(caption = "Men's Parallel Bars Simulation Results ", col.names = c("Athlete", "Golds", "Silvers", "Bronzes", "Total Medals")) |>
  kable_styling(font_size = 9, latex_options = "HOLD_position")
```

```{r}
#Creates country variable
PB_m_simul$Country <- factor(sub(".+_([A-Z]+)", "\\1", PB_m_simul$unique_id))
#adds medal weight variable
PB_m_simul$Medal_Weight <- (PB_m_simul$Golds*3) + (PB_m_simul$Silvers*2) + (PB_m_simul$Bronzes*1)
#adds apparatus to facet by later on in visuals
PB_m_simul$Apparatus <- "PB"
PB_m_simul
```

```{r}
#Joins all men's medal results table for facet wrapping

#HAVE TO EVENTUALLY ADD VT1 and VT2!!
tot_m_simul <- bind_rows(FX_m_simul, VT_m_simul,PH_m_simul, HB_m_simul,SR_m_simul, PB_m_simul)
tot_m_simul <- tot_m_simul %>% 
  mutate(USA = as.factor(ifelse(Country == "USA", TRUE, FALSE)))
tot_m_simul
```

# Objective 1) EDA

## Women
```{r}
#Prioritizing Gold Medals
ggplot(data = tot_w_simul, aes(x = USA, y = Golds, color = USA)) + geom_point() + facet_wrap(~Apparatus) + labs(title = "Women's Simulated Gold Medals by Country (USA vs non-USA)", subtitle = "by Apparatus") +coord_flip()

#Prioritizing Total Medals
ggplot(data = tot_w_simul, aes(x = USA, y = Total_Medals, color = USA)) + geom_point() + facet_wrap(~Apparatus) + labs(title = "Women's Simulated Total Medals by Country (USA vs non-USA)", subtitle = "by Apparatus") +coord_flip()

#Prioritizing Weighted Medals
ggplot(data = tot_w_simul, aes(x = USA, y = Medal_Weight, color = USA)) + geom_point() + facet_wrap(~Apparatus) + labs(title = "Women's Simulated Weighted Medals by Country (USA vs non-USA)", subtitle = "by Apparatus") +coord_flip()

```
```{r}
#Top 5 athletes by apparatus for gold count
tot_w_simul %>% 
  group_by(Apparatus) %>% 
  slice_max(order_by = Golds, n = 5)

#Top 5 athletes by apparatus for total medal count
tot_w_simul %>% 
  group_by(Apparatus) %>% 
  slice_max(order_by = Total_Medals, n = 5)

#Top 5 athletes by apparatus for weighted medal count
tot_w_simul %>% 
  group_by(Apparatus) %>% 
  slice_max(order_by = Medal_Weight, n = 5)


#total proportion for each medal metric
tot_w_simul %>% 
  group_by(USA) %>% 
  summarise(sumGolds = sum(Golds))

tot_w_simul %>% 
  group_by(USA) %>% 
  summarise(sumTot = sum(Total_Medals))

tot_w_simul %>% 
  group_by(USA) %>% 
  summarise(sumWeighted = sum(Medal_Weight))
```

For the women's simulation when looking at the top 5 athletes by:

*Gold Medal Count* for each apparatus there are 11 out of 20 from the US:
- balance beam (BB): 2
- floor exercise (FX): 3
- uneven bars (UB): 2
- vault (VT): 4

USA makes up 58% of the total women's gold medals in the simulation.

*Total Medal Count* for each apparatus there are 10 out of 21 from the US:
- balance beam (BB): 2  
- floor exercise (FX): 2
- uneven bars (UB): 2
- vault (VT): 4

USA makes up 49% of the total women's medals in the simulation.

*Weighted Medal Count* for each apparatus there are 9 out of 21 from the US:
- balance beam (BB): 2  
- floor exercise (FX): 2
- uneven bars (UB): 2
- vault (VT): 3

USA makes up 52% of the weight of women's medals in the simulation.

## Men
```{r}
#Prioritizing Gold Medals
ggplot(data = tot_m_simul, aes(x = USA, y = Golds, color = USA)) + geom_point() + facet_wrap(~Apparatus) + labs(title = "Men's Simulated Gold Medals by Country (USA vs non-USA)", subtitle = "by Apparatus") +coord_flip()

#Prioritizing Total Medals
ggplot(data = tot_m_simul, aes(x = USA, y = Total_Medals, color = USA)) + geom_point() + facet_wrap(~Apparatus) + labs(title = "Men's Simulated Total Medals by Country (USA vs non-USA)", subtitle = "by Apparatus") +coord_flip()

#Prioritizing Weighted Medals
ggplot(data = tot_m_simul, aes(x = USA, y = Medal_Weight, color = USA)) + geom_point() + facet_wrap(~Apparatus) + labs(title = "Men's Simulated Weighted Medals by Country (USA vs non-USA)", subtitle = "by Apparatus") +coord_flip()

```
```{r}
#Top 5 athletes by apparatus for gold count
tot_m_simul %>% 
  group_by(Apparatus) %>% 
  slice_max(order_by = Golds, n = 5)

#Top 5 athletes by apparatus for total medal count
tot_m_simul %>% 
  group_by(Apparatus) %>% 
  slice_max(order_by = Total_Medals, n = 5)

#Top 5 athletes by apparatus for weighted medal count
tot_m_simul %>% 
  group_by(Apparatus) %>% 
  slice_max(order_by = Medal_Weight, n = 5)

#total proportion for each medal metric
tot_m_simul %>% 
  group_by(USA) %>% 
  summarise(sumGolds = sum(Golds))

tot_m_simul %>% 
  group_by(USA) %>% 
  summarise(sumTot = sum(Total_Medals))

tot_m_simul %>% 
  group_by(USA) %>% 
  summarise(sumWeighted = sum(Medal_Weight))
```

For the men's simulation when looking at the top 5 athletes by:

*Gold Medal Count* for each apparatus there are 5 out of 34 from the US (including ties):
- floor exercise (FX): 0
- high bar (HB): 0
- parallel bars (PB): 3
- pommel horse (PH): 0
- still rings (SR): 0
- vault (VT): 2

USA makes up 23% of the total men's gold medals in the simulation.

*Total Medal Count* for each apparatus there are 3 out of 34 from the US:
- floor exercise (FX): 1
- high bar (HB): 0
- parallel bars (PB): 0
- pommel horse (PH): 0
- still rings (SR): 0
- vault (VT): 2

USA makes up 25% of the total men's medals in the simulation.

*Weighted Medal Count* for each apparatus there are 5 out of 32 from the US:
- floor exercise (FX): 1
- high bar (HB): 0
- parallel bars (PB): 1
- pommel horse (PH): 0
- still rings (SR): 0
- vault (VT): 3

USA makes up 24% of the weight of men's medals in the simulation.
